Practical Optional Types for Clojure

### 2015-06-29 small.tex
typo

We provide a formal model of the Typed Clojure type system
incorporating these and other features, with a proof of
soundness. Additionally, Typed Clojure is now in use by numerous
corporations and developers working with Clojure, and we report on 
a quantiative analysis of the use of the features described in this
paper in two substantial code bases.

>>>>

We provide a formal model of the Typed Clojure type system
incorporating these and other features, with a proof of
soundness. Additionally, Typed Clojure is now in use by numerous
corporations and developers working with Clojure, and we report on 
a quantitative analysis of the use of the features described in this
paper in two substantial code bases.
